---
title: "Assignment2"
author: "Nickie Mitch"
date: "9/14/2020"
output: html_document
---

## Load libraries

```{r load libaries, message=FALSE}
library(tidyverse)
library(ggplot2)
```

## Load Household-level Data
```{r load hh data, message=FALSE}
hh_data <- read_csv("household_data_me.csv")
```

## Distribution of a continuous variable (household income over the past 12 months)

### Summary Statistics

```{r summary statistics, message=FALSE}
HINCP_Summary <- summary(hh_data$HINCP)

HINCP_Summary
```

### Standard Deviation
```{r standard deviation, message=FALSE}
sd(hh_data$HINCP)
```

### 95% Confidence Interval
```{r 95 confidence interval, message=FALSE}
conf_int <- t.test(hh_data$HINCP)

conf_int

conf_int$conf.int[1]

conf_int$conf.int[2]
```

### Histogram
```{r histogram, message=FALSE}
hist(hh_data$HINCP)
```

### Fancy Histogram
```{r fancy histogram, message=FALSE}
ggplot(hh_data, aes(x = HINCP)) +
  geom_histogram()
```

## Proportions of a categorical variable (internet access)

### List all possible values
```{r list values, message=FALSE}
unique(hh_data$ACCESS_label)
```

### Number of observations by category
```{r number of observations, message=FALSE}
table(hh_data$ACCESS_label)
```

### Observations to proportions
```{r proportions, message=FALSE}
table(hh_data$ACCESS_label) / sum(table(hh_data$ACCESS_label))
```
```{r mean and confidence interval individually, message=FALSE}
mean(hh_data$ACCESS_label == "Yes, by paying a cell phone company or Internet service provider")

t.test(hh_data$ACCESS_label == "Yes, by paying a cell phone company or Internet service provider")
```
## Distribution of a continuous variable (number of related children in this household)

## Distribution of a continuous variable (number of persons in this household)

## Proportions of a categorical variable (detailed household language)
