---
title: "Assignment 5"
author: "Nickie Mitch"
date: "10/5/2020"
output: html_document
---
### Load Libraries
```{r load libraries, message=FALSE}
library(tidyverse)
library(jtools)
library(DescTools)
library(interactions)
library(knitr)
```

### Load Data
 My sample is made up of all households in Maine who had incomes over the past 12 months.
```{r load data, message=FALSE}
hh_data <- read_csv("simple_hh_data3.csv") %>%
  mutate(n_Adults=NP-NRC) %>%
  filter(HINCP>0)
```


### Initial Regression Model (Logistic Regression from Assignment 4)
```{r model}
model <- glm(INTERNET ~ HINCP + LANGUAGE + NRC + n_Adults, 
            data = hh_data, family = "binomial")
summary(model)
PR_sq_1 <- PseudoR2(model, c("Nagelkerke")) 
#I use Nagelkerke's Pseudo R2 because it is displayed in the export_summs() output later.
AIC_1 <- AIC(model)

PR_sq_1
AIC_1
```

### Regression Model with Log-Transform
As in the tutorial, I log-transformed income because percentage changes are more relevant than absolute changes.
```{r model 2}
model2 <- glm(INTERNET ~ log(HINCP) + LANGUAGE + NRC + n_Adults, 
            data = hh_data, family = "binomial")
summary(model2)
PR_sq_2 <- PseudoR2(model2, c("Nagelkerke"))
AIC_2 <- AIC(model2)

PR_sq_2
AIC_2
```

### Regression Model with Interaction Terms
I expected that primary household language may impact household income, that number of adults may impact number of related children, and that number of adults may impact houshold income. I added these interactions to my model. 

```{r model 3}
model3 <- glm(INTERNET ~ HINCP + LANGUAGE + NRC + n_Adults + LANGUAGE:HINCP + n_Adults:NRC + HINCP:n_Adults, 
            data = hh_data, family = "binomial")
summary(model3)
PR_sq_3 <- PseudoR2(model3, c("Nagelkerke"))
AIC_3 <- AIC(model3)

PR_sq_3
AIC_3
```
### Comparison Plot of Models
A higher Nagelkerke's PseudoR2 value indicates better model fit. According to Nagelkerke's PseudoR2, Model 3 is the best fit. 

```{r - pseudor2}
Nagelkerke_PseudoR2 <- tibble(model = c(1, 2, 3),
                   Pseudo_R_square = c(PR_sq_1, PR_sq_2, PR_sq_3))
ggplot(Nagelkerke_PseudoR2, aes(x = model, y = Pseudo_R_square)) +
  geom_line() +
  scale_x_continuous(name = "",
                   breaks = breaks <- seq(1, 4, by = 1),
                   labels = paste("Model", breaks)) +
  scale_y_continuous(name = "Nagelkerke's PseudoR2") +
  theme_bw()
```

A lower Akaike information criterion (AIC) value indicates better model fit. According to AIC, Model 3 is the best fit.
```{r - AIC}
AIC <- tibble(model = c(1, 2, 3),
                   AIC = c(AIC_1, AIC_2, AIC_3))
ggplot(AIC, aes(x = model, y = AIC)) +
  geom_line() +
  scale_x_continuous(name = "",
                   breaks = breaks <- seq(1, 4, by = 1),
                   labels = paste("Model", breaks)) +
  scale_y_continuous(name = "AIC") +
  theme_bw()

```

### Exporting Regression Results 
```{r export}
coeff_names <- c("Annual Income" = "HINCP",
                "French\n(compared to English)" = "LANGUAGEFrench",
                "Spanish\n(compared to English)" = "LANGUAGESpanish",
                "Some other language\n(compared to English)" = "LANGUAGESome other language",
                "Number of Related Children" = "NRC",
                "Number of Adults" = "n_Adults",
                "Interaction:\nspeaking french and income" = 
                    "HINCP:LANGUAGEFrench",
                "Interaction:\nspeaking spanish and income" = 
                    "HINCP:LANGUAGESome other language",
                "Interaction:\nspeaking some other language and income" = 
                    "HINCP:LANGUAGEFrench",
                 "Interaction:\nnumber of related children and number of adults" = 
                    "NRC:n_Adults",
                 "Interaction:\nnumber of adults and income" = 
                    "HINCP:n_Adults")


export_summs(model, model3, 
             error_format = "(p = {p.value})",
             error_pos = "same",
             model.names = c("Initial model", "Preferred model"),
             coefs = coeff_names)
```


### Visualizing Regression Results
```{r 95ci plot}
coeff_desc <- c("Interaction:\nspeaking french and income" = 
                    "HINCP:LANGUAGEFrench",
                "Interaction:\nspeaking spanish and income" = 
                    "HINCP:LANGUAGESome other language",
                "Interaction:\nspeaking some other language and income" = 
                    "HINCP:LANGUAGEFrench",
                 "Interaction:\nnumber of related children and number of persons" = 
                    "NRC:n_Adults",
                 "Interaction:\nnumber of persons and income" = 
                    "HINCP:n_Adults",
                "Annual Income" = "HINCP",
                "French\n(compared to English)" = "LANGUAGEFrench",
                "Spanish\n(compared to English)" = "LANGUAGESpanish",
                "Some other language\n(compared to English)" = "LANGUAGESome other language",
                "Number of Related Children" = "NRC",
                "Number of Adults" = "n_Adults")


plot_coefs(model3, 
           coefs = coeff_desc,
           plot.distributions = TRUE,
           rescale.distributions = TRUE) +
  scale_x_continuous(name = "Effect on Probability of Having Internet Access")
```

```{r interaction plot 1}
interact_plot(model3, pred = HINCP, modx = LANGUAGE, interval = TRUE) +
  scale_x_continuous(name = "Annual income (thousands)",
                     limits = c(0, 500000),
                     breaks = breaks <- seq(0, 500000, by = 50000),
                     labels = paste("$", 
                                    prettyNum(breaks/1000, big.mark = "'"),
                                    sep = "")) +
  scale_y_continuous(name = "Probability of Having Internet Access",
                     breaks = seq(0, 1, by = 0.1)) +
  scale_color_discrete(name = "") +
  scale_linetype_discrete(name = "") +
  scale_fill_discrete(name = "") 
```

```{r interaction plot 2}
interact_plot(model3, pred = HINCP, modx = n_Adults, legend.main = "Number of Adults", interval = TRUE) +
scale_x_continuous(name = "Annual income (thousands)",
                     limits = c(0, 500000),
                     breaks = breaks <- seq(0, 500000, by = 50000),
                     labels = paste("$", 
                                    prettyNum(breaks/1000, big.mark = "'"),
                                    sep = "")) +
  scale_y_continuous(name = "Probability of Having Internet Access",
                     breaks = seq(0, 1, by = 0.05))

```

```{r interaction plot 3}
interact_plot(model3, pred = NRC, modx = n_Adults, legend.main = "Number of Adults", interval = TRUE) +
scale_x_continuous(name = "Number of Related Children",
                     limits = c(0, 11),
                     breaks = breaks <- seq(0, 11, by = 1),
                     labels = paste(prettyNum(breaks, big.mark = "'"),
                                    sep = "")) +
  scale_y_continuous(name = "Probability of Having Internet Access",
                     breaks = seq(0, 1, by = 0.01))
```


### Interpretation 

