---
title: "Assignment 3"
author: "Nickie Mitch"
date: "9/18/2020"
output: html_document
---

## Load Libraries
```{r load libraries, message=FALSE}
library(tidyverse)
library(ggplot2)
```

## Load Data
```{r load data, message=FALSE}
hh_data <- read_csv("household_data_me.csv") %>%
  mutate(LANGUAGE = case_when(
    HHLANP_label=="Japanese"~"Some other language",
    HHLANP_label=="English only household"~"English",
    HHLANP_label=="Korean"~"Some other language",
    HHLANP_label=="German"~"Some other language",
    HHLANP_label=="Other Native North American languages"~"Some other language",
    HHLANP_label=="Arabic"~"Some other language",
    HHLANP_label=="Thai"~"Some other language",
    HHLANP_label=="Italian"~"Some other language",
    HHLANP_label=="Chinese"~"Some other language",
    HHLANP_label=="Pennsylvania German"~"Some other language",
    HHLANP_label=="Urdu"~"Some other language",
    HHLANP_label=="Cebuano"~"Some other language",
    HHLANP_label=="Tagalog"~"Some other language",
    HHLANP_label=="Romanian"~"Some other language",
    HHLANP_label=="Other Bantu Languages"~"Some other language",
    HHLANP_label=="Bosnian"~"Some other language",
    HHLANP_label=="Hindi"~"Some other language",
    HHLANP_label=="Portuguese"~"Some other language",
    HHLANP_label=="Mandarin"~"Some other language",
    HHLANP_label=="Cantonese"~"Some other language",
    HHLANP_label=="Filipino"~"Some other language",
    HHLANP_label=="Bengali"~"Some other language",
    HHLANP_label=="Somali"~"Some other language",
    HHLANP_label=="Serbian"~"Some other language",
    HHLANP_label=="Russian"~"Some other language",
    HHLANP_label=="Vietnamese"~"Some other language",
    HHLANP_label=="Lithuanian"~"Some other language",
    HHLANP_label=="Farsi"~"Some other language",
    HHLANP_label=="Turkish"~"Some other language",
    HHLANP_label=="Tamil"~"Some other language",
    HHLANP_label=="Finnish"~"Some other language",
    HHLANP_label=="Telugu"~"Some other language",
    HHLANP_label=="Swahili"~"Some other language", 
    HHLANP_label=="Spanish"~"Spanish",
    HHLANP_label=="French"~"French"),
  INTERNET = case_when(
    ACCESS_label=="Yes, by paying a cell phone company or Internet service provider"~"Yes",
    ACCESS_label=="No access to the Internet at this house, apartment, or mobile home"~"No",
    ACCESS_label=="Yes, without paying a cell phone company or Internet service provider"~"Yes"))
```

## Relationship Between Household Income (HINCP) and Number of Persons (NP) 
These are two continuous variables. 

```{r relationship HINCP AND NP}
correlation <- cor.test(hh_data$HINCP, hh_data$NP)

correlation
```
```{r plot HINCP and NP}
options(scipen=10000)
ggplot(hh_data, aes(x = HINCP, y = NP)) +
  geom_point(size = 0.5, alpha = 0.25, position = "jitter") +
  geom_smooth() +
  theme_bw() +
  scale_x_continuous(name = "Household Income Over the Past 12 Months") +
  scale_y_continuous(name = "Number of Persons", 
                     breaks = seq(0, 10, by = 1),
                     labels = paste(prettyNum(seq(0, 10, by = 1),
                                              big.mark = ","))) +
  annotate(geom = "text", x = 0, y = 10, 
           label = paste("Correlation (95-percent confidence):",
                         prettyNum(correlation$conf.int[1]), 
                         "to",
                         prettyNum(correlation$conf.int[2])),
           hjust = 0)
```

## Relationship Between Household Income (HINCP) and Number of Related Children (NRC) 
These are two continuous variables. 

```{r relationship HINCP AND NRC}
correlation <- cor.test(hh_data$HINCP, hh_data$NRC)

correlation
```
```{r plot HINCP and NRC}
options(scipen=10000)
ggplot(hh_data, aes(x = HINCP, y = NRC)) +
  geom_point(size = 0.5, alpha = 0.25, position = "jitter") +
  geom_smooth() +
  theme_bw() +
  scale_x_continuous(name = "Household Income Over the Past 12 Months") +
  scale_y_continuous(name = "Number of Related  Children", 
                     breaks = seq(0, 10, by = 1),
                     labels = paste(prettyNum(seq(0, 10, by = 1),
                                              big.mark = ","))) +
  annotate(geom = "text", x = 0, y = 10, 
           label = paste("Correlation (95-percent confidence):",
                         prettyNum(correlation$conf.int[1]), 
                         "to",
                         prettyNum(correlation$conf.int[2])),
           hjust = 0)
```


## Relationship Between Household Income (HINCP) and Internet Access (INTERNET)
These are a continuous variable and a binary variable.

```{r HINCP and INTERNET}
difference1 = t.test(HINCP ~ INTERNET == "Yes",
                    data = hh_data)

difference1
```

```{r plot HINCP AND INTERNET}
ggplot(hh_data, aes(x = INTERNET, y = HINCP)) +
  geom_violin() +
  theme_bw() +
  scale_x_discrete(name = "Internet Access",
                   labels = c("No", "Yes")) +
   scale_y_continuous(name = "Household Income Over the Past 12 Months", 
                     breaks = seq(0, 500000, by = 100000),
                     labels = paste("$", prettyNum(seq(0, 500000, by = 100000)))) +
  annotate(geom = "text", x = 1.5, y = 700000, size = 3,
           label = paste("Difference in means\n(95% confidence):\n$",
                         prettyNum(abs(difference1$conf.int[2]), 
                                   digits = 0), " to $",
                         prettyNum(abs(difference1$conf.int[1]), 
                                   digits = 0),
                         sep = "")) +
  annotate(geom = "text", x = 1, y = difference1$estimate[1], size = 3,
           label = paste("Mean (95% confidence):\n$",
                         prettyNum(difference1$estimate[1], digits = 0))) +
  annotate(geom = "text", x = 2, y = difference1$estimate[2], size = 3,
           label = paste("Mean (95% confidence):\n$",
                         prettyNum(difference1$estimate[2], digits = 0)))
```

## Relationship Between Household Income (HINCP) and Household Language (LANGUAGE)
These are a continuous variable and a categorical variable.

```{r relationship HINCP and LANGUAGE}
anova <- aov(HINCP ~ LANGUAGE, data = hh_data)

summary(anova)
```

```{r plot HINCP and LANGUAGE}
ggplot(hh_data, aes(x = LANGUAGE, y = HINCP)) +
  geom_boxplot() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_x_discrete(name = "Primary Household Language") +
  scale_y_continuous(name = "Household Income Over the Past 12 Months", 
                      breaks = seq(0, 500000, by = 100000),
                     labels = paste("$", 
                                    prettyNum(seq(0, 500000, by = 100000),
                                              big.mark = ","))) 
                                             
```

## Relationship Between Numper of Persons (NP) and Household Language (LANGUAGE)
These are a continuous variable and a categorical variable.

```{r relationship NP and LANGUAGE}
anova <- aov(NP ~ LANGUAGE, data = hh_data)

summary(anova)
```

```{r plot NP and LANGUAGE}
ggplot(hh_data, aes(x = LANGUAGE, y = NP)) +
  geom_boxplot() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_x_discrete(name = "Primary Household Language") +
  scale_y_continuous(name = "Number of Persons in Household", 
                      breaks = seq(0, 10, by = 1),
                     labels = paste((seq(0, 10, by = 1)))) 
                                             
```

## Relationship Between Number of Related Children (NRC) and Household Language (LANGUAGE)
These are a continuous variable and a categorical variable.

```{r relationship NRC and LANGUAGE}
anova <- aov(NRC ~ LANGUAGE, data = hh_data)

summary(anova)
```

```{r plot NRC and LANGUAGE}
ggplot(hh_data, aes(x = LANGUAGE, y = NRC)) +
  geom_boxplot() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_x_discrete(name = "Primary Household Language") +
  scale_y_continuous(name = "Number of Related Children in Household", 
                      breaks = seq(0, 15, by = 1),
                     labels = paste((seq(0, 15, by = 1)))) 
                                             
```

## Relationship Between Internet Access (INTERNET) and Household Language (LANGUAGE)
These are a continuous variable and a categorical variable.

```{r relationship INTERNET and LANGUAGE}
chi_sq <- chisq.test(hh_data$LANGUAGE, hh_data$INTERNET == 
                       "Yes") 

chi_sq
```
Instructions for making this mosaic plot were found at https://stackoverflow.com/questions/19233365/how-to-create-a-marimekko-mosaic-plot-in-ggplot2 
```{r plot INTERNET and LANGUAGE}
df <- hh_data %>%
  group_by(LANGUAGE, INTERNET) %>%
  summarise(count = n()) %>%
  mutate(prop = count/sum(count)) %>%
  ungroup()


ggplot(df, aes(x = INTERNET, y = prop, fill = LANGUAGE)) +
  geom_bar(stat = "identity", position = "fill", colour = "black") +
  facet_grid(~INTERNET, scales = "free_x", space = "free_x") +
  scale_fill_brewer(palette = "RdYlGn") +
  ggtitle("Internet Access") + 
  theme_void() 
```

## Relationship Between Number of Persons (NP) and Number of Related Children (NRC) 
These are two continuous variables. 

```{r relationship NP AND NRC}
correlation <- cor.test(hh_data$NP, hh_data$NRC)

correlation
```

```{r plot}
options(scipen=10000)
ggplot(hh_data, aes(x = NP, y = NRC)) +
  geom_point(size = 0.5, alpha = 0.25, position = "jitter") +
  geom_smooth() +
  theme_bw() +
  scale_x_continuous(name = "Number of Persons",
                     breaks = seq(0, 15, by = 1),
                     labels = paste(prettyNum(seq(0, 15, by = 1),
                                              big.mark = ",")))+
  scale_y_continuous(name = "Number of Related Children", 
                     breaks = seq(0, 15, by = 1),
                     labels = paste(prettyNum(seq(0, 15, by = 1),
                                              big.mark = ","))) +
  annotate(geom = "text", x = 0, y = 10, 
           label = paste("Correlation (95-percent confidence):",
                         prettyNum(correlation$conf.int[1]), 
                         "to",
                         prettyNum(correlation$conf.int[2])),
           hjust = 0)
```


## Relationship Between Number of Persons (NP) and Internet Access (INTERNET)
These are a continuous variable and a binary variable.

```{r NP and INTERNET}
difference2 = t.test(NP ~ INTERNET == "Yes",
                    data = hh_data)

difference2
```

```{r plot NP AND INTERNET}
ggplot(hh_data, aes(x = INTERNET, y = NP)) +
  geom_violin() +
  theme_bw() +
  scale_x_discrete(name = "Internet Access",
                   labels = c("No", "Yes")) +
   scale_y_continuous(name = "Number of Persons", 
                     breaks = seq(0, 15, by = 1),
                     labels = paste(prettyNum(seq(0, 15, by = 1)))) +
  annotate(geom = "text", x = 1.5, y = 7, size = 3,
           label = paste("Difference in means\n(95% confidence):\n",
                         prettyNum(abs(difference2$conf.int[2]), 
                                   digits = 0), " to ",
                         prettyNum(abs(difference2$conf.int[1]), 
                                   digits = 0),
                         sep = "")) +
  annotate(geom = "text", x = 1, y = difference2$estimate[1], size = 3,
           label = paste("Mean (95% confidence):\n",
                         prettyNum(difference2$estimate[1], digits = 0))) +
  annotate(geom = "text", x = 2, y = difference2$estimate[2], size = 3,
           label = paste("Mean (95% confidence):\n",
                         prettyNum(difference2$estimate[2], digits = 0)))
```


## Relationship Between Number of Related Children (NRC) and Internet Access (INTERNET)
These are a continuous variable and a binary variable.

```{r NRC and INTERNET}
difference3 = t.test(NRC ~ INTERNET == "Yes",
                    data = hh_data)

difference3
```

```{r plot NRC AND INTERNET}
ggplot(hh_data, aes(x = INTERNET, y = NP)) +
  geom_violin() +
  theme_bw() +
  scale_x_discrete(name = "Internet Access",
                   labels = c("No", "Yes")) +
   scale_y_continuous(name = "Number of Related Children", 
                     breaks = seq(0, 15, by = 1),
                     labels = paste(prettyNum(seq(0, 15, by = 1)))) +
  annotate(geom = "text", x = 1.5, y = 7, size = 3,
           label = paste("Difference in means\n(95% confidence):\n",
                         prettyNum(abs(difference3$conf.int[2]), 
                                   digits = 0), " to ",
                         prettyNum(abs(difference3$conf.int[1]), 
                                   digits = 0),
                         sep = "")) +
  annotate(geom = "text", x = 1, y = difference3$estimate[1], size = 3,
           label = paste("Mean (95% confidence):\n",
                         prettyNum(difference3$estimate[1], digits = 0))) +
  annotate(geom = "text", x = 2, y = difference3$estimate[2], size = 3,
           label = paste("Mean (95% confidence):\n",
                         prettyNum(difference3$estimate[2], digits = 0)))
```